Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-22 article.Rmd
motor traffic

1. Measures such as point closures or contraflow cycle lanes, which can be used to promote 'filtered permeability', a strategy in which street networks are redesigned so that routes for cyclists are faster and more direct than routes for drivers. An example of this is  [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets].
2. Measures to close roads entirely to particular classes of vehicle, including time-limited closures, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020].
3. Measures to reallocate space on wide roads to create new cycleways or to widen pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->

>>>>

1. Measures such as point closures or contraflow cycle lanes, which can be used to promote 'filtered permeability', a strategy in which street networks are redesigned so that routes for cyclists are faster and more direct than routes for drivers. An example of this is  [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets].
2. Measures to close roads entirely to motor traffic or to particular classes of vehicle, either permanently or at certain times of day, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020].
3. Measures to reallocate space on wide roads to create new cycleways or to widen pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->
